---
title: "Data Analysis #2 Version 2 (75 points total)"
author: "Zhang, Taoran"
output:
  html_document: default
---

```{r setup, include = FALSE}
# DO NOT ADD OR REVISE CODE HERE
knitr::opts_chunk$set(echo = FALSE, eval = TRUE)

```


-----

##Data Analysis #2

```{r analysis_setup1, message = FALSE, warning = FALSE}

# Perform the following steps to start the assignment.
 
# 1) Load/attach the following packages via library():  flux, ggplot2, gridExtra, moments, rockchalk, car.
# NOTE:  packages must be installed via install.packages() before they can be loaded.

library(flux)
library(ggplot2)
library(gridExtra)
library(moments)
library(rockchalk) # base R code replaces requirement for this package
library(car)

# 2) Use the "mydata.csv" file from Assignment #1 or use the file posted on the course site.  Reading
# the files into R will require sep = "" or sep = " " to format data properly.  Use str() to check file
# structure.

mydata <- read.csv("mydata.csv", sep = ",")
# mydata <- read.csv(file.path("c:...", "mydata.csv"), sep = ",")
# mydata <- read.csv(file.path("c:/Rabalone/", "mydata.csv"), sep = ",")

str(mydata)

```

### Test Items starts from here - There are 10 sections - total of 75 points ##############

##### Section 1: (5 points)

(1)(a) Form a histogram and QQ plot using RATIO. Calculate skewness and kurtosis using 'rockchalk.' Be aware that with 'rockchalk', the kurtosis value has 3.0 subtracted from it which differs from the 'moments' package. 

```{r Part_1a}
par(mfrow=c(1,2))
hist(mydata$RATIO)
qqnorm(mydata$RATIO)
qqline(mydata$RATIO)
rockchalk::skewness(mydata$RATIO)
rockchalk::kurtosis(mydata$RATIO)

```

(1)(b) Tranform RATIO using *log10()* to create L_RATIO (Kabacoff Section 8.5.2, p. 199-200). Form a histogram and QQ plot using L_RATIO. Calculate the skewness and kurtosis. Create a boxplot of L_RATIO differentiated by CLASS.

```{r Part_1b}
L_RATIO<-log10(mydata$RATIO)
mydata$L_RATIO<-L_RATIO
par(mfrow=c(1,2))
hist(L_RATIO)
qqnorm(L_RATIO)
qqline(L_RATIO)
rockchalk::skewness(L_RATIO)
rockchalk::kurtosis(L_RATIO)
boxplot(L_RATIO~CLASS,data = mydata)

```

(1)(c) Test the homogeneity of variance across classes using *bartlett.test()* (Kabacoff Section 9.2.2, p. 222). 

```{r Part_1c}
bartlett.test(RATIO~CLASS,data = mydata)
bartlett.test(L_RATIO~CLASS,data = mydata)

```

**Essay Question: Based on steps 1.a, 1.b and 1.c, which variable RATIO or L_RATIO exhibits better conformance to a normal distribution with homogeneous variances across age classes?  Why?** 

***Answer: L_Ratio exhibits better confirmance to normal distribution and it has a homogeneous variance across age class. The difference in normality can be observed via the histogram shapes, and the QQ plot-the logged number show a much more normally distibuted shape. The skewness and kurtosis also show significant difference. ***
***The Barlett test of homogeneity of variance yield significant difference (inhomogeneous) (p value less than 0.01) for Ratio by Class. And the test for L_Ratio yield p value of 0.53- we cannot reject the null hypothesis and thus the logged ratio shows homogeneous variance across age classes. ***


##### Section 2 (10 points) ###############################

(2)(a) Perform an analysis of variance with *aov()* on L_RATIO using CLASS and SEX as the independent variables (Kabacoff chapter 9, p. 212-229). Assume equal variances. Perform two analyses. First, fit a model with the interaction term CLASS:SEX. Then, fit a model without CLASS:SEX. Use *summary()* to obtain the analysis of variance tables (Kabacoff chapter 9, p. 227).

```{r Part_2a}
aov1<-aov(L_RATIO~CLASS*SEX,data = mydata)
aov2<-aov(L_RATIO~CLASS+SEX,data = mydata)
summary(aov1)
summary(aov2)

```

**Essay Question:  Compare the two analyses.  What does the non-significant interaction term suggest about the relationship between L_RATIO and the factors CLASS and SEX?**

***Answer: The model with the interaction shows a pvalue of 0.87 for the interaction between Class and Sex, meaning that there is no strong interaction between the two variables. For this reason, we can safely perform modeling without the interaction term. As both analyses show, there are significant correlation between Class and L_Ratio, as well as Sex and L_Ratio. We can consider both variables affect the L_Ratio and they don’t have a strong interaction with each other.***

(2)(b) For the model without CLASS:SEX (i.e. an interaction term), obtain multiple comparisons with the *TukeyHSD()* function. Interpret the results at the 95% confidence level (*TukeyHSD()* will adjust for unequal sample sizes). 

```{r Part_2b}
TukeyHSD(aov2)

```

**Additional Essay Question:  first, interpret the trend in coefficients across age classes. What is this indicating about L_RATIO?  Second, do these results suggest male and female abalones can be combined into a single category labeled as 'adults?' If not, why not?**

***Answer: The p adj value across different classes are mostly below 0.05, only A2-A1 is insignificant. That indicates basically all levels of Class affect L_RATIO (except difference between A1 and A2). The HSD test on SEX yields significant p value for Infant-Male and Infant Female, and male vs female is not significant. That means whether an abalone is infant has significant affect on L_Ratio, whereas male or female does not yield a significant difference: so we can combine male and female as ‘adults’***


######  Section 3: (10 points) ##################

(3)(a1) We combine "M" and "F" into a new level, "ADULT". (While this could be accomplished using *combineLevels()* from the 'rockchalk' package, we use base R code because many students do not have access to the rockchalk package.) This necessitated defining a new variable, TYPE, in mydata which had two levels:  "I" and "ADULT". 

```{r Part_3a1}
# here we show how to define the new variable TYPE using only base R functions (no need for outside packages)
mydata$TYPE <- character(nrow(mydata))  # initialize the TYPE column as all blanks
for (i in seq(along = mydata$SEX)) {
  mydata$TYPE[i] <- 'I'
  if (mydata$SEX[i] == 'M' || mydata$SEX[i] == 'F') mydata$TYPE[i] <- 'ADULT'
}
mydata$TYPE <- factor(mydata$TYPE)
cat('\nCheck on definition of TYPE object (should be an integer): ', typeof(mydata$TYPE))
cat('\nmydata$TYPE is treated as a factor: ', is.factor(mydata$TYPE), '\n')
table(mydata$SEX, mydata$TYPE)

```
(3)(a2)  Present side-by-side histograms of VOLUME. One should display infant volumes and, the other, adult volumes. 

```{r Part_3a2}
par(mfrow=c(1,2))
hist(mydata$VOLUME[mydata$TYPE=='I'],main='infant volume', xlab = 'volume')
hist(mydata$VOLUME[mydata$TYPE=='ADULT'],main='adult volume', xlab = 'volume')
```


**Essay Question: Compare the histograms.  How do the distributions differ? Are there going to be any difficulties separating infants from adults based on VOLUME?**

***Answer: The infant volume has an obvious right-tailed distribution- most infants have low volume (<400). The adult volume is more normally distributed with a center at about 400. There will be difficulty to separate infants from  adults based on volume, as there is still significant overlap in volume from 100—400.***

(3)(b) Create a scatterplot of SHUCK versus VOLUME and a scatterplot of their base ten logarithms, labeling the variables as L_SHUCK and L_VOLUME. Please be aware the variables, L_SHUCK and L_VOLUME, present the data as orders of magnitude (i.e. VOLUME = 100 = 10^2 becomes L_VOLUME = 2). Use color to differentiate CLASS in the plots. Repeat using color to differentiate by TYPE. 

```{r Part_3b}
par(mfrow=c(2,2))
mydata$L_SHUCK<-log10(mydata$SHUCK)
mydata$L_VOLUME<-log10(mydata$VOLUME)

g1<-ggplot(mydata,aes(x=VOLUME,y = SHUCK,color=CLASS))+geom_point()
g2<-ggplot(mydata,aes(x=L_VOLUME,y = L_SHUCK,color=CLASS))+geom_point()
g3<-ggplot(mydata,aes(x=VOLUME,y = SHUCK,color=TYPE))+geom_point()
g4<-ggplot(mydata,aes(x=L_VOLUME,y = L_SHUCK,color=TYPE))+geom_point()
grid.arrange(g1, g2,g3,g4, nrow = 2)
```

**Additional Essay Question:  Compare the two scatterplots. What effect(s) does log-transformation appear to have on the variability present in the plot?  What are the implications for linear regression analysis? Where do the various CLASS levels appear in the plots? Where do the levels of TYPE appear in the plots?**

***Answer: In both sets of plots, the log-transformed variable shows less variability and more linear shape in general. One implication is that log-transforming variables help us to find significant linear models, with stronger correlation. As color coded dots show, lower class have lower volume and adults have larger volume than infants.***


######   Section 4: (5 points) ###################################

(4)(a1) Since abalone growth slows after class A3, infants in classes A4 and A5 are considered mature and candidates for harvest. Reclassify the infants in classes A4 and A5 as ADULTS. This reclassification could have been achieved using *combineLevels()*, but only on the abalones in classes A4 and A5. We will do this recoding of the TYPE variable using base R functions. We will use this recoded TYPE variable, in which the infants in A4 and A5 are reclassified as ADULTS, for the remainder of this data analysis assignment. 

```{r Part_4a1}
for (i in seq(along = mydata$TYPE)) {
  if (mydata$CLASS[i] == 'A4' || mydata$CLASS[i] == 'A5') mydata$TYPE[i] <- 'ADULT'
}
mydata$TYPE <- factor(mydata$TYPE)
cat('\nCheck on redefinition of TYPE object (should be an integer): ', typeof(mydata$TYPE))
cat('\nmydata$TYPE is treated as a factor: ', is.factor(mydata$TYPE), '\n')
cat('\nThree-way contingency table for SEX, CLASS, and TYPE:\n')
print(table(mydata$SEX, mydata$CLASS, mydata$TYPE))
```

(4)(a2) Regress L_SHUCK as the dependent variable on L_VOLUME, CLASS and TYPE (Kabacoff Section 8.2.4, p. 178-186, the Data Analysis Video #2 and Black Section 14.2). Use the multiple regression model: L_SHUCK ~ L_VOLUME + CLASS + TYPE. Apply *summary()* to the model object to produce results.

```{r Part_4a2}
model<-lm(L_SHUCK ~ L_VOLUME + CLASS + TYPE, data=mydata)
summary(model)



```

**Essay Question:  Interpret the trend in CLASS levelcoefficient estimates? (Hint:  this question is not asking if the estimates are statistically significant. It is asking for an interpretation of the pattern in these coefficients, and how this pattern relates to the earlier displays).**

***Answer:A pattern in the p value of different classes show that the larger a class gets, the more significant (smaller p value) the correlations are. This pattern matches the prior scatter plot display, in which points are color coded by classes. Classes A1 and A2 relatively spread across a range of shucks, where as the higher classes tend to cluster tighter towards high volume high shuck.***

**Additional Essay Question:  Is TYPE an important predictor in this regression? (Hint:  This question is not asking if TYPE is statistically significant, but rather how it compares to the other independent variables in terms of its contribution to predictions of L_SHUCK for harvesting decisions.)  Explain your conclusion.**

***Answer: I think type is not as an important predictor in this regression. One reason being that other variables like L_Volume and Class shows much smaller p value-meaning that the correlation is more significant. Besides, the first column of the lm output shows the slope coefficient. The L_Volume has a slope almost equal to 1, indicating an linear relationship. L_Volume would be a more important predictor than type.***

-----

The next two analysis steps involve an analysis of the residuals resulting from the regression model in (4)(a) (Kabacoff Section 8.2.4, p. 178-186, the Data Analysis Video #2).

-----

###### Section 5: (5 points) #################################

(5)(a) If "model" is the regression object, use model$residuals and construct a histogram and QQ plot. Compute the skewness and kurtosis. Be aware that with 'rockchalk,' the kurtosis value has 3.0 subtracted from it which differs from the 'moments' package. 

```{r Part_5a}
par(mfrow=c(1,2))
hist(model$residuals)
qqnorm(model$residuals)
qqline(model$residuals)
rockchalk::skewness(model$residuals)
rockchalk::kurtosis(model$residuals)

```

(5)(b) Plot the residuals versus L_VOLUME, coloring the data points by CLASS and, a second time, coloring the data points by TYPE. Keep in mind the y-axis and x-axis may be disproportionate which will amplify the variability in the residuals. Present boxplots of the residuals differentiated by CLASS and TYPE (These four plots can be conveniently presented on one page using *par(mfrow..)* or *grid.arrange()*. Test the homogeneity of variance of the residuals across classes using *bartlett.test()* (Kabacoff Section 9.3.2, p. 222).  

```{r Part_5b}
par(mfrow=c(2,2))
mydata$residuals<-model$residuals
g1<-ggplot(mydata,aes(x=L_VOLUME,y = residuals,color=CLASS))+geom_point()
g2<-ggplot(mydata,aes(x=L_VOLUME,y = residuals,color=TYPE))+geom_point()
g3<-ggplot(mydata,aes(x=CLASS,y = residuals))+geom_boxplot()
g4<-ggplot(mydata,aes(x=TYPE,y = residuals))+geom_boxplot()
grid.arrange(g1, g2,g3,g4, nrow = 2)
bartlett.test(residuals~CLASS,data = mydata)

```

**Essay Question:  What is revealed by the displays and calculations in (5)(a) and (5)(b)? Does the model 'fit'?  Does this analysis indicate that L_VOLUME, and ultimately VOLUME, might be useful for harvesting decisions? Discuss.**  

***Answer: The display of residuals of the model, as well as the skewness and kurtosis calculations, show a normally distributed pattern. That is one of the indications that the regression model of L_Volume, class and type is fit. The plots in 5b shows no obvious pattern of residuals across different class and types. The box plots are also centered at 0 and are well-balanced. These graphs help to show that the model “fits”***

-----

There is a tradeoff faced in managing abalone harvest. The infant population must be protected since it represents future harvests. On the other hand, the harvest should be designed to be efficient with a yield to justify the effort. This assignment will use VOLUME to form binary decision rules to guide harvesting. If VOLUME is below a "cutoff" (i.e. a specified volume), that individual will not be harvested. If above, it will be harvested. Different rules are possible.

The next steps in the assignment will require consideration of the proportions of infants and adults harvested at different cutoffs. For this, similar "for-loops" will be used to compute the harvest proportions. These loops must use the same values for the constants min.v and delta and use the same statement "for(k in 1:10000)."  Otherwise, the resulting infant and adult proportions cannot be directly compared and plotted as requested. Note the example code supplied below.

-----

#### Section 6: (5 points) ########################

(6)(a) A series of volumes covering the range from minimum to maximum abalone volume will be used in a "for loop" to determine how the harvest proportions change as the "cutoff" changes. Code for doing this is provided.

```{r Part_6a}

idxi <- mydata$TYPE == "I"
idxa <- mydata$TYPE == "ADULT"

max.v <- max(mydata$VOLUME)
min.v <- min(mydata$VOLUME)
delta <- (max.v - min.v)/10000
prop.infants <- numeric(10000)
prop.adults <- numeric(10000)
volume.value <- numeric(10000)

total.infants <- sum(idxi)  
total.adults <- sum(idxa)

for (k in 1:10000) { 
	value <- min.v + k*delta
	volume.value[k] <- value
	prop.infants[k] <- sum(mydata$VOLUME[idxi] <= value)/total.infants
	prop.adults[k] <-  sum(mydata$VOLUME[idxa] <= value)/total.adults
}

# prop.infants shows the impact of increasing the volume cutoff for
# harvesting. The following code shows how to "split" the population at
# a 50% harvest of infants.

n.infants <- sum(prop.infants <= 0.5)
split.infants <- min.v + (n.infants + 0.5)*delta  # This estimates the desired volume.
split.infants

n.adults <- sum(prop.adults <= 0.5)
split.adults <- min.v + (n.adults + 0.5)*delta
split.adults

```

(6)(b) Present a plot showing the infant proportions and the adult proportions versus volume.value. Compute the 50% "split" volume.value for each and show on the plot.   

```{r Part_6b}
plot(y=prop.adults,x=volume.value,col='blue',xlab='volume',ylab='proportion',type='l')
points(x=volume.value,y =prop.infants,col='red',type='l' )
legend('bottom',c('adults','infants'),col=c('blue','red'),lwd=3)
abline(h=0.5)
abline(v=split.adults)
abline(v=split.infants)
text(x=split.adults+20, y=0.4,'384.51')
text(x=split.infants+20, y=0.4,'133.82')
```

**Essay Question:  The two 50% "split" values serve a descriptive purpose illustrating the difference between the populations. What do these values suggest regarding possible cutoffs for harvesting?** 

***Answer: The 50% split volume for adult and infant harvest rate is showing obvious difference. The infant split volume is much lower than that of adult, as infant have generally less volume than adults. A general goal of harvesting is to harvest higher percentage of adults and lower percentage of infant (smaller the better). And this graph show us a trade off between the two values. To achieve harvesting over half of adults and less than half of infants- the harvest cutoff should be between 133.82 and 384.51.***

-----

This part will address the determination of a volume.value corresponding to the observed maximum difference in harvest percentages of adults and infants. To calculate this result, the vectors of proportions from item (6) must be used. These proportions must be converted from "not harvested" to "harvested" proportions by using (1 - prop.infants) for infants, and (1 - prop.adults) for adults. The reason the proportion for infants drops sooner than adults is that infants are maturing and becoming adults with larger volumes.

-----

###### Section 7: (10 points)  #######################

(7)(a) Evaluate a plot of the difference ((1 - prop.adults) - (1 - prop.infants)) versus volume.value. Compare to the 50% "split" points determined in (6)(a). There is considerable variability present in the peak area of this plot. The observed "peak" difference may not be the best representation of the data. One solution is to smooth the data to determine a more representative estimate of the maximum difference.

```{r Part_7a}
difference<-(1 - prop.adults) - (1 - prop.infants)
plot(y=difference,x=volume.value,main='Difference in Harvest Proportion unsmooth',col='red',type='l')


```

(7)(b) Since curve smoothing is not studied in this course, code is supplied below. Execute the following code to create a smoothed curve to append to the plot in (a). The procedure is to individually smooth (1-prop.adults) and (1-prop.infants) before determining an estimate of the maximum difference. 

```{r Part_7b}

y.loess.a <- loess(1 - prop.adults ~ volume.value, span = 0.25,
	family = c("symmetric"))
y.loess.i <- loess(1 - prop.infants ~ volume.value, span = 0.25,
	family = c("symmetric"))
smooth.difference <- predict(y.loess.a) - predict(y.loess.i)

```

(7)(c) Present a plot of the difference ((1 - prop.adults) - (1 - prop.infants)) versus volume.value with the variable smooth.difference superimposed. Determine the volume.value corresponding to the maximum smoothed difference (Hint:  use *which.max()*). Show the estimated peak location corresponding to the cutoff determined.

```{r Part_7c}
plot(y=difference,x=volume.value,main='Difference in Harvest Proportion',col='red',type='l')
lines(y=smooth.difference,x=volume.value,col='blue',type='l')
maxdiff.vol<-min.v + which.max(smooth.difference)*delta
abline(v=maxdiff.vol)
text('volume=262.143',y=0.4,x=maxdiff.vol+40)

```

(7)(d) What separate harvest proportions for infants and adults would result if this cutoff is used? Show the separate harvest proportions (NOTE:  the adult harvest proportion is the "true positive rate" and the infant harvest proportion is the "false positive rate").

Code for calculating the adult harvest proportion is provided.

```{r Part_7d}
adtharvest<-(1 - prop.adults)[which.max(smooth.difference)]  # [1] 0.7416332
infantharvest<-(1-prop.infants)[which.max(smooth.difference)]
adtharvest
infantharvest
```

-----

There are alternative ways to determine cutoffs. Two such cutoffs are described below.

-----

######  Section 8: (10 points)  ###################

(8)(a) Harvesting of infants in CLASS "A1" must be minimized. The smallest volume.value cutoff that produces a zero harvest of infants from CLASS "A1" may be used as a baseline for comparison with larger cutoffs. Any smaller cutoff would result in harvesting infants from CLASS "A1."  

Compute this cutoff, and the proportions of infants and adults with VOLUME exceeding this cutoff. Code for determining this cutoff is provided. Show these proportions.

```{r Part_8a}
A1cutoff<-volume.value[volume.value > max(mydata[mydata$CLASS == "A1" &
  mydata$TYPE == "I", "VOLUME"])][1] # [1] 206.786
A1cutoff
A1infantrate<-nrow(mydata[mydata$TYPE=='I'&mydata$VOLUME>A1cutoff,])/sum(mydata$TYPE=='I');A1infantrate
A1adtrate<-nrow(mydata[mydata$TYPE=='ADULT'&mydata$VOLUME>A1cutoff,])/sum(mydata$TYPE=='ADULT');A1adtrate


```

(8)(b) Another cutoff is one for which the proportion of adults not harvested equals the proportion of infants harvested. This cutoff would equate these rates; effectively, our two errors:  'missed' adults and wrongly-harvested infants. This leaves for discussion which is the greater loss:  a larger proportion of adults not harvested or infants harvested?  This cutoff is 237.7383. Calculate the separate harvest proportions for infants and adults using this cutoff. Show these proportions.  Code for determining this cutoff is provided.  

```{r Part_8b}
min.diff.cutoff<-volume.value[which.min(abs(prop.adults - (1-prop.infants)))] # [1] 237.6391
min.diff.cutoff
Min.Diff.infantrate<-nrow(mydata[mydata$TYPE=='I'&mydata$VOLUME>min.diff.cutoff,])/sum(mydata$TYPE=='I');Min.Diff.infantrate
Min.Diff.adtrate<-nrow(mydata[mydata$TYPE=='ADULT'&mydata$VOLUME>min.diff.cutoff,])/sum(mydata$TYPE=='ADULT');Min.Diff.adtrate
```


##### Section 9: (5 points) ###########

(9)(a) Construct an ROC curve by plotting (1 - prop.adults) versus (1 - prop.infants). Each point which appears corresponds to a particular volume.value. Show the location of the cutoffs determined in (7) and (8) on this plot and label each. 

```{r Part_9}
plot(y=1-prop.adults,x=1-prop.infants,col='blue',main='ROC Curve', type='l',xlab='infant harvest rate', ylab = 'adult harvest rate')
abline(a=0,b=1)
points(y=c(0.7416332,0.8259705,0.7817938),x=c(0.1764706,0.2871972,0.2179931),col='red')
text(x=0.18,y=0.65,'max diff vol= 262.14' )
text(x=0.29,y=0.9,'Zero A1 vol= 206.786' )
text(x=0.4,y=0.78,'equal error vol= 237.6' )

```

(9)(b) Numerically integrate the area under the ROC curve and report your result. This is most easily done with the *auc()* function from the "flux" package.   Areas-under-curve, or AUCs, greater than 0.8 are taken to indicate good discrimination potential. 

```{r Part_9b}
auc(y=1-prop.adults,x=1-prop.infants)


```


##### Section 10: (10 points) ###################

(10)(a) Prepare a table showing each cutoff along with the following:
 	1) true positive rate (1-prop.adults),
 	2) false positive rate (1-prop.infants),
 	3) harvest proportion of the total population
 	
```{r Part_10} 	
table <- matrix(c(262.143,0.742,0.176,0.584,206.786,0.826,0.287,0.676,237.639,0.782,0.218,0.625),ncol=4,byrow=TRUE)
colnames(table) <- c("Volume","TPR","FPR","PropYield")
rownames(table) <- c("max.difference","zero.A1.Infants","equalerror")
table<-as.table(table)
table

```
 	
**Essay Question: Based on the ROC curve, it is evident a wide range of possible "cutoffs" exist. Compare and discuss the three cutoffs determined in this assignment.**   

***Answer: The three cutoff points shown on the ROC curve represents three different strategies, each with a compromise. The maximum difference in harvest rate has the highest cutoff volume and Zero A1 strategy has the lowest cutoff volume. The max. difference strategy harvest least percentage of adults but also least percentage of infants (lowest false positive rate). The zero A1 strategy is the opposite—resulting in a highest true positive but also highest false positive. The Equal Error cutoff is a compromise between max diff. and zero A1 cutoff.***



**Final Essay Question:  Assume you are expected to make a presentation of your analysis to the investigators How would you do so?  Consider the following in your answer:**

1. Would you make a specific recommendation or outline various choices and tradeoffs?
2. What qualifications or limitations would you present regarding your analysis?
3. If it is necessary to proceed based on the current analysis, what suggestions would you have for implementation of a cutoff?  4)  What suggestions would you have for planning future abalone studies of this type? 

***Answer: I would present the ROC curve and use it to illustrate the tradeoff between adult harvest rate (true positive) and the infant harvest rate (false negative). The three cutoff strategies will be presented and compared as case studies to illustrate how one rate would affect the other.        ***
***I will also present the infant proportion and adult proportions versus volume. That helps me to demonstrate the difference and overlap of the two different abalone populations. The vertical lines can be used to show how different cutoffs involve different tradeoffs. One limitation I will mention is that only volume is used as a variable to distinguish harvest or not- the linear model of Shuck to other variables showed other potential cutoff candidates.          ***
***If it is necessary to proceed based on current analysis, I would suggest the equal error cutoff, with a volume=237.6, as it is a compromise of two other strategies—considerable amount of adults will be harvested (over 78%) and the infant harvest rate is just above 20%.***
***For future studies of abalone, I would suggest looking for more potential metrics as variables, so that we have more candidates for modeling and a higher chance of finding better harvest standards.  It could also be helpful to build more complex models beyond multiple linear regression- for example 2nd order models. We can also try to use 2-variable combinations as cutoff standards, for example (volume, class).***





