---
title: 'Data Analysis Assignment #1 (50 points total)'
author: "Zhang, Taoran"
output:
  html_document: default
---

```{r setup, include = FALSE}
# DO NOT ADD OR REVISE CODE HERE
knitr::opts_chunk$set(echo = FALSE, eval = TRUE)

```

-----

The following code chunk will:

(a) load the "ggplot2", "gridExtra" and "knitr" packages, assuming each has been installed on your machine,
(b) read-in the abalones dataset, defining a new data frame, "mydata,"
(c) return the structure of that data frame, and
(d) calculate new variables, VOLUME and RATIO.

Do not include package installation code in this document. Packages should be installed via the Console or 'Packages' tab. You will also need to download the abalones.csv from the course site to a known location on your machine. Unless a *file.path()* is specified, R will look to directory where this .Rmd is stored when knitting.

```{r analysis_setup1, message = FALSE, warning = FALSE}

# a) Load the ggplot2 and gridExtra packages.

library(ggplot2)
library(gridExtra)
library(knitr)

# b) Use read.csv() to read the abalones.csv into R, assigning the data frame to "mydata."

mydata <- read.csv("abalones.csv", sep = ",")


# c) Use the str() function to verify the structure of "mydata." You should have 1036 observations
# of eight variables.

str(mydata)

# d) Define two new variables, VOLUME and RATIO. Use the following statements to define VOLUME and
# RATIO as variables appended to the data frame "mydata."

mydata$VOLUME <- mydata$LENGTH * mydata$DIAM * mydata$HEIGHT
mydata$RATIO <- mydata$SHUCK / mydata$VOLUME

```

-----

### Test Items starts from here - There are 6 sections ##########################

##### Section 1: (6 points) Summarizing the data.

(1)(a) (1 point) Use *summary()* to obtain and present descriptive statistics from mydata.  Use table() to present a frequency table using CLASS and RINGS. There should be 115 cells in the table you present.  

```{r Part_1a}
summary(mydata)
table(mydata$CLASS,mydata$RINGS)


```

**Question (1 point):  Briefly discuss the variable types and distributional implications such as potential skewness and outliers.**

***The dataset contains 10 columns, two of them are factors (sex and class), the rest are numbers (rings column contains integer). According to the summary, serveral variables could contain outliers. For example there are outlier values for WHOLE-both min and max are far from the 1st and 3rd quantile. The table also seem to display a correlation between class and ring- the class number increases as rings increase. ***

(1)(b) (1 point) Generate a table of counts using SEX and CLASS. Add margins to this table (Hint: There should be 15 cells in this table plus the marginal totals. Apply *table()* first, then pass the table object to *addmargins()* (Kabacoff Section 7.2 pages 144-147)).  Lastly, present a barplot of these data; ignoring the marginal totals.  

```{r Part_1b}
sex_class<-table(mydata$SEX,mydata$CLASS)
addmargins(sex_class)
barplot(sex_class, beside = TRUE,col=c("darkblue","red",'green'),legend = c('Female','Infant','Male'),xlab = 'Class',ylab = 'Count')
```

**Essay Question (2 points):  Discuss the sex distribution of abalones.  What stands out about the distribution of abalones by CLASS?**

***Answer:  An obvious trend of sex distribution is that the proportion of infant is very high in A1 nad A2 classes and the proportions are low in A3, A4 and A5. The male abalones are consistently higher than female in all classes, however the different becomes smaller in A4 and A5. ***

(1)(c) (1 point) Select a simple random sample of 200 observations from "mydata" and identify this sample as "work." Use *set.seed(123)* prior to drawing this sample. Do not change the number 123. Note that *sample()* "takes a sample of the specified size from the elements of x." We cannot sample directly from "mydata." Instead, we need to sample from the integers, 1 to 1036, representing the rows of "mydata." Then, select those rows from the data frame (Kabacoff Section 4.10.5 page 87). 

Using "work", construct a scatterplot matrix of variables 2-6 with *plot(work[, 2:6])* (these are the continuous variables excluding VOLUME and RATIO). The sample "work" will not be used in the remainder of the assignment. 

```{r Part_1c}
set.seed(123)
work<-mydata[sample(c(1:1036),size=200),]
plot(work[, 2:6])
```

-----

##### Section 2: (5 points) Summarizing the data using graphics.

(2)(a) (1 point) Use "mydata" to plot WHOLE versus VOLUME. Color code data points by CLASS.

```{r Part_2a}
ggplot(data=mydata,aes(x=WHOLE,y=VOLUME))+
  geom_point(aes(color = CLASS))

```


(2)(b) (2 points) Use "mydata" to plot SHUCK versus WHOLE with WHOLE on the horizontal axis. Color code data points by CLASS. As an aid to interpretation, determine the maximum value of the ratio of SHUCK to WHOLE.  Add to the chart a straight line with zero intercept using this maximum value as the slope of the line. If you are using the 'base R' *plot()* function, you may use *abline()* to add this line to the plot. Use *help(abline)* in R to determine the coding for the slope and intercept arguments in the functions. If you are using ggplot2 for visualizations, *geom_abline()* should be used.

```{r Part_2b}
ggplot(data=mydata,aes(y=SHUCK,x=WHOLE))+
  geom_point(aes(color = CLASS))+geom_abline(slope = max(mydata$SHUCK/mydata$WHOLE))

```

**Essay Question (2 points):  How does the variability in this plot differ from the plot in (a)?  Compare the two displays.  Keep in mind that SHUCK is a part of WHOLE.  Consider the location of the different age classes.**

***Answer: Plot (a) displays volume versus whole weight and shows a positive correlation between the two variables, the points are spread out for whole over 200, indicating a relatively large variability. The variability of plot (b) is significantly smaller than plot (a), especially in the region of Whole wight from 200 to 300.The points are colored by classes and we observe that higher class abalones tend to have higher whole weight, as well as shuck weight and volume ***

-----

##### Section 3: (8 points) Getting insights about the data using graphs.

(3)(a) (2 points) Use "mydata" to create a multi-figured plot with histograms, boxplots and Q-Q plots of RATIO differentiated by sex. This can be done using *par(mfrow = c(3,3))* and base R or *grid.arrange()* and ggplot2. The first row would show the histograms, the second row the boxplots and the third row the Q-Q plots. Be sure these displays are legible.  

```{r Part_3a}
par(mfrow = c(3,3))
femaledata<-mydata[mydata$SEX=='F',]
maledata<-mydata[mydata$SEX=='M',]
infdata<-mydata[mydata$SEX=='I',]
hist(femaledata$RATIO,main='Female Ratio',col='red')
hist(maledata$RATIO,main='Male Ratio',col='blue')
hist(infdata$RATIO,main='Infant Ratio',col='green')
boxplot(femaledata$RATIO,main='Female Ratio',col='red')
boxplot(maledata$RATIO,main='Male Ratio',col='blue')
boxplot(infdata$RATIO,main='Infant Ratio',col='green')
qqnorm(femaledata$RATIO,main='Female Ratio',col='red')
qqline(femaledata$RATIO,main='Female Ratio',col='red')
qqnorm(maledata$RATIO,main='Male Ratio',col='blue')
qqline(maledata$RATIO,main='Male Ratio',col='blue')
qqnorm(infdata$RATIO,main='Infant Ratio',col='green')
qqline(infdata$RATIO,main='Infant Ratio',col='green')
```

**Essay Question (2 points): Compare the displays.  How do the distributions compare to normality? Take into account the criteria discussed in the sync sessions to evaluate non-normality.**

***Answer: The histogram and qq plots show that the distributuions of ratio, across three sex types are right skewed, as the qq plot departs from the staight line. This right skew distribution can also be told from the outliers in box plots***

(3)(b) (2 points) Use the boxplots to identify RATIO outliers (mild and extreme both) for each sex. Present the abalones with these outlying RATIO values along with their associated variables in "mydata" (Hint:  display the observations by passing a data frame to the kable() function).  

```{r Part_3b}
femaleout<-boxplot(femaledata$RATIO,plot = FALSE)$out
maleout<-boxplot(maledata$RATIO,plot = FALSE)$out
infout<-boxplot(infdata$RATIO,plot = FALSE)$out
femalerow<-which(femaledata$RATIO %in% femaleout)
femalerow<-as.numeric(rownames(femaledata[femalerow,]))
malerow<-which(maledata$RATIO %in% maleout)
malerow<-as.numeric(rownames(maledata[malerow,]))
infrow<-which(infdata$RATIO %in% infout)
infrow<-as.numeric(rownames(infdata[infrow,]))
rows<-c(infrow,femalerow,malerow)
kable(mydata[rows,])


```

**Essay Question (2 points):  What are your observations regarding the results in (3)(b)?**

***Answer: There are more infant in the outliers than female or male. And class A1 and A3 comprise most of the outliers. The number of female and male outliers is similar.***

-----

##### Section 4: (8 points) Getting insights about possible predictors.

(4)(a) (3 points) With "mydata," display side-by-side boxplots for VOLUME and WHOLE, each differentiated by CLASS There should be five boxes for VOLUME and five for WHOLE. Also, display side-by-side scatterplots:  VOLUME and WHOLE versus RINGS. Present these four figures in one graphic:  the boxplots in one row and the scatterplots in a second row. Base R or ggplot2 may be used.


```{r Part_4a}
par(mfrow=c(2,2))
boxplot(mydata$VOLUME~mydata$CLASS,ylab='Volume')
boxplot(mydata$WHOLE~mydata$CLASS,ylab='Whole')
plot(mydata$VOLUME,mydata$RINGS,ylab='Volume',xlab='rings')
plot(mydata$WHOLE,mydata$RINGS,ylab='Whole',xlab='rings')
```

**Essay Question (5 points) How well do you think these variables would perform as predictors of age?  Explain.**

***Answer: The volume and whole vs. Class boxplox show a pattern that as age increase (CLass from A1--A5), we tend to observe higher median volume and whole weight. However, I also notice that the median volume and whole weight of A5 is actually lower than that of A4. That makes volume and whole weight poor predictors of class (which roughly reflect age), for class over A3. The scatter plot also shows a vague trend that volume and whole weight increase as age increases. However, the trend is very vague and there are many data points with similar volume or weight but at very different ages (for example when volem is around 10) That makes both volume and whole weight poor predictors of age.***

-----

##### Section 5: (12 points) Getting insights regarding different groups in the data.

(5)(a) (2 points) Use *aggregate()* with "mydata" to compute the mean values of VOLUME, SHUCK and RATIO for each combination of SEX and CLASS. Then, using *matrix()*, create matrices of the mean values. Using the "dimnames" argument within *matrix()* or the *rownames()* and *colnames()* functions on the matrices, label the rows by SEX and columns by CLASS. Present the three matrices (Kabacoff Section 5.6.2, p. 110-111). The *kable()* function is useful for this purpose.  You do not need to be concerned with the number of digits presented.

```{r Part_5a}
volsum <- aggregate(VOLUME~CLASS+SEX,data = mydata, mean)
shucksum <- aggregate(SHUCK~CLASS+SEX,data = mydata, mean)
RATIOsum <- aggregate(RATIO~CLASS+SEX,data = mydata, mean)
tbl1<-matrix(data=volsum$VOLUME,byrow = TRUE,nrow = 3)
tbl2<-matrix(data=shucksum$SHUCK,byrow = TRUE,nrow = 3)
tbl3<-matrix(data=RATIOsum$RATIO,byrow = TRUE,nrow = 3)
rownames(tbl1)<-c('Female','Infant','Male')
colnames(tbl1)<-levels(mydata$CLASS)
rownames(tbl2)<-c('Female','Infant','Male')
colnames(tbl2)<-levels(mydata$CLASS)
rownames(tbl3)<-c('Female','Infant','Male')
colnames(tbl3)<-levels(mydata$CLASS)
kable(tbl1)
kable(tbl2)
kable(tbl3)
```

(5)(b) (3 points) Present three graphs. Each graph should include three lines, one for each sex. The first should show mean RATIO versus CLASS; the second, mean VOLUME versus CLASS; the third, mean SHUCK versus CLASS. This may be done with the 'base R' *interaction.plot()* function or with ggplot2 using *grid.arrange()*.

```{r Part_5b, fig.width = 9}
g1<-ggplot(data = RATIOsum, aes(x = CLASS, y = RATIO, group = SEX, 
  colour = SEX))+ geom_line()+
  ggtitle("Mean RATIO vs CLASS")
g2<-ggplot(data = volsum, aes(x = CLASS, y = VOLUME, group = SEX, 
  colour = SEX))+ geom_line()+
  ggtitle("Mean VOLUME vs CLASS")
g3<-ggplot(data = shucksum, aes(x = CLASS, y = SHUCK, group = SEX, 
  colour = SEX))+ geom_line()+
  ggtitle("Mean SHUCK vs CLASS")
grid.arrange(g1,g2,g3,ncol=1)

```

**Essay Question (2 points):  What questions do these plots raise?  Consider aging and sex differences.**

***Answer: (Enter your answer here.)***

5(c) (3 points) Present four boxplots using *par(mfrow = c(2, 2)* or *grid.arrange()*. The first line should show VOLUME by RINGS for the infants and, separately, for the adult; factor levels "M" and "F," combined. The second line should show WHOLE by RINGS for the infants and, separately, for the adults. Since the data are sparse beyond 15 rings, limit the displays to less than 16 rings. One way to accomplish this is to generate a new data set using subset() to select RINGS < 16.  Use ylim = c(0, 1100) for VOLUME and ylim = c(0, 400) for WHOLE.  If you wish to reorder the displays for presentation purposes or use ggplot2 go ahead.

```{r Part_5c}
infdata<-mydata[mydata$SEX=='I'& mydata$RINGS<16,]
adultdata<-mydata[mydata$SEX!='I'& mydata$RINGS<16,]
par(mfrow = c(2, 2))
boxplot(infdata$VOLUME~infdata$RINGS,ylim = c(0, 1100),main='Volume vs Rings for infants')
boxplot(adultdata$VOLUME~adultdata$RINGS,ylim = c(0, 1100),main='Volume vs Rings for adults')
boxplot(infdata$WHOLE~infdata$RINGS,ylim = c(0, 400),main='whole vs Rings for infants')
boxplot(adultdata$WHOLE~adultdata$RINGS,ylim = c(0, 400),main='whole vs Rings for adults')

```

**Essay Question (2 points):  What do these displays suggest about abalone growth?  Also, compare the infant and adult displays.  What differences stand out?**

***Answer: The line chart shows a general trend that the ratio decreases as abalone ages and volume and shuck weight increases as age increase. It is also worth noticing that the ratio of male and female are approximately the same across different classes. And we observe the mean volume and shuck weight of female abalones are consistently higher than that of male abalones. (The infant data for class A4 and A5 is rare so not compared with the other two.) The boxplot for infact vs adult of volume and whole weight shows a similar shaped trend. The volume and whole weight both increases as age increase and flat out around 11rings. However, the volume and whole weight of adult abalones are significantly larger than infants for age over 6 rings. Adult data also displays larger variability for higher age abalones.***

-----

##### Section 6: (11 points) Conclusions from the Exploratory Data Analysis (EDA).

**Conclusions**


**Essay Question 1) (5 points)	Based solely on these data, what are plausible statistical reasons that explain the failure of the original study? Consider to what extent physical measurements may be used for age prediction.**

***Answer: The exploratory display of the data is not sufficient to support a single indicator for age. The volume and weight (whole or shuck) of abalones are correlated to the age and class. But the correlation is not strong enough to build an effective regression model to predict age based on volume, weight or ratio.  A major reason for failure of original study is that there is a large variance in each parameters across ages. For example, as we can see in the scatter plot in 4a, samples with same volume and weight spread across a wide range of ages. This large variability creates a large uncertainty when we use these measures as basis for prediction—in linear regression models the R value would be low.  The attempt to sort data into infant vs adult and find prediction parameters was not very successful either- the variance is still high for each sub-dataset.***

**Essay Question 2) (3 points) Do not refer to the abalone data or study.  If you were presented with an overall histogram and summary statistics from a sample of some population or phenomenon and no other information, what questions might you ask before accepting them as representative of the sampled population or phenomenon?**

***Answer: I will first observe the distribution of the sample data, based on the histogram. I am interested in the skewness of the data and see if the distribution matches the expectation of population distribution. If the overall population distribution is normal and the displayed graph shows left or right skewness, there may be some bias in the sampling process. It is also helpful to see the median, quantiles and maximum/ minimum of the sample data. A sample with large variance or many extreme outliers should not be accepted as representative of population.   ***

**Essay Question 3)  (3 points)	Do not refer to the abalone data or study.  What do you see as difficulties analyzing data derived from observational studies? Can causality be determined?  What might be learned from such studies?**

***Answer: The observational studies can hardly yield definitive or quantitative conclusions of a population. We can get an idea of sample distribution through different graphs; some graphs may help to reveal correlations between different parameters. However, we cannot yield any results of causality without quantitative data analysis of a carefully controlled experiment. It is very helpful in getting the big picture of data collected and identifying proper candidates for further analysis. For example a strong correlation between two parameters will indicate possible good predictors so that researchers can build models with a focus on these parameters.***

